Reduced diversity and increased specialization of Alaska salmon fishermen:

### 2016-10-28 salmon/paper/salmon_paper.Rmd
update

seak = read.csv("../../salmon/data-generated/stopha_table32.csv")
pws = read.csv("../../salmon/data-generated/stopha_table33.csv")
kodiak = read.csv("../../salmon/data-generated/stopha_table35.csv")

seak = melt(seak, id.vars = c("Year"))
pws = melt(pws, id.vars = c("Year"))
kodiak = melt(kodiak, id.vars = c("Year"))

seak$region = "Southeast"
pws$region = "Prince William Sound"
kodiak$region = "Kodiak"

seak$value[is.na(seak$value)] = 0
pws$value[is.na(pws$value)] = 0
kodiak$value[is.na(kodiak$value)] = 0

dat = bind_rows(seak, pws)
dat = bind_rows(dat, kodiak)

@@

dat$col = as.numeric(as.factor(dat$species))
ggplot(dat, aes(Year, value)) +
  geom_area(aes(fill = species), position = "stack") +
  xlab("Year") + ylab("Harvest of hatchery produced salmon (millions)") +
  scale_fill_manual(values = c('Chinook'=cbPalette[1], 'Chum'=cbPalette[2], 
    'Coho'=cbPalette[3], 'Pink'=cbPalette[4], 'Sockeye'=cbPalette[5]), name="Species",
    labels =c("Chinook","Sockeye","Coho","Pink","Chum")) + 
  facet_wrap(~region, scale="free_y")
```

>>>>

seak_hatch = read.csv("../../salmon/data-generated/seak_hatcheryHarvest.csv")
pws_hatch = read.csv("../../salmon/data-generated/pws_hatcheryHarvest.csv")
kodiak_hatch = read.csv("../../salmon/data-generated/kodiak_hatcheryHarvest.csv")

seak_hatch = melt(seak_hatch, id.vars = c("Year"))
pws_hatch = melt(pws_hatch, id.vars = c("Year"))
kodiak_hatch = melt(kodiak_hatch, id.vars = c("Year"))

seak_hatch$region = "Southeast"
pws_hatch$region = "Prince William Sound"
kodiak_hatch$region = "Kodiak"

seak_hatch$value[is.na(seak_hatch$value)] = 0
pws_hatch$value[is.na(pws_hatch$value)] = 0
kodiak_hatch$value[is.na(kodiak_hatch$value)] = 0

dat = bind_rows(seak_hatch, pws_hatch)
dat = bind_rows(dat, kodiak_hatch)

@@

dat$col = as.numeric(as.factor(dat$species))
ggplot(dat, aes(Year, value)) +
  geom_area(aes(fill = species), position = "stack") +
  xlab("Year") + ylab("Harvest of hatchery produced salmon (millions)") +
  scale_fill_manual(values = c('Chinook'=cbPalette[1], 'Chum'=cbPalette[2], 
    'Coho'=cbPalette[3], 'Pink'=cbPalette[4], 'Sockeye'=cbPalette[5]), name="Species",
    labels =c("Chinook","Sockeye","Coho","Pink","Chum")) + 
  facet_wrap(~region, scale="free_y")

# bring in total harvest data (hatchery + wild)
#seak = read.csv("../../salmon/data-generated/stopha_table32.csv")
pws = read.csv("../../salmon/data-generated/pws_totalHarvest.csv")
kodiak = read.csv("../../salmon/data-generated/kodiak_totalHarvest.csv")

pws = melt(pws[,c("Year","Chinook","Sockeye","Coho","Pink","Chum")], id.vars = c("Year"))
kodiak = melt(kodiak[,c("Year","Chinook","Sockeye","Coho","Pink","Chum")], id.vars = c("Year"))
pws$region = "Prince William Sound"
kodiak$region = "Kodiak"
datall = bind_rows(pws,kodiak)
names(datall)[which(names(datall)=="variable")]="species"
datall$value = datall$value / 1000000
names(datall)[which(names(datall)=="value")]="totalharvest"

# join in hatchery harvest with total harvest
dat = left_join(dat, datall)

dat$percent_hatch = dat$value/dat$totalharvest
dat$percent_hatch[is.na(dat$percent_hatch)] = 0
dat$percent_hatch[dat$percent_hatch>1] = 1
# chinook chum coho pink sock
#cbPalette <- c("#009E73", "#4B2E83", "#999999", "#CC79A7", "#D55E00")

ggplot(dat[dat$region%in%c("Kodiak", "Prince William Sound") & dat$Year < 2015,], aes(Year, percent_hatch, color=species)) +
  geom_line() +
  xlab("Year") + 
  ylab("Proportion of hatchery harvest") +
  facet_wrap(~region, scale="free_y")
#  
#  scale_fill_manual(values = c('Chinook'=cbPalette[1], 'Chum'=cbPalette[2], 
#    'Coho'=cbPalette[3], 'Pink'=cbPalette[4], 'Sockeye'=cbPalette[5]), name="Species",
#    labels =c("Chinook","Sockeye","Coho","Pink","Chum")) +
